---
title: "Introduction to homer"
author: "Bill Zichos"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to homer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Use the homer package with R to collect and analyze publicly available residential real estate data.  The plot below represents daily home values over the course of a couple months for a home I just sold.  Actually, the buying and selling of my home was the inspiration for this package.  I wanted to make sure I had the best available information for decision making.  *314 Wood Hollow* was listed for sale in early October and a sale was final on December 15.

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
library("homer")
library("ggplot2")
library("xml2")
library("glue")
library("lubridate")
library("stringr")

ts <- paste0(
    year(Sys.Date())
    , str_sub(paste0("0", month(Sys.Date())), -2)
    , str_sub(paste0("0", day(Sys.Date())), -2))
zillow_dir <- system.file(package = "homer", "extdata")
```

```{r, fig.width=7.2, fig.height=2, echo=FALSE}
homer::plot_zillow_directory(zillow_dir, strip_font_size = 12, nudge_y = 800, value_size = 2.6)
```

```{r libraries, eval=FALSE}
```


### Step 1. Obtain Zillow API Key

Follow the instructions to [Get Started](https://www.zillow.com/howto/api/APIOverview.htm) with the Zillow API and obtain an API key.  Save the key your .Renviron startup file.

```{r, eval=FALSE}
# Open the .Renviron file.
file.edit("~/.Renviron")
```

```
# Add the following line:
ZILLOWAPI="[Your API key here]"

# Save the file.
```

### Step 2. Gather Data

Find the Zillow-ID for a property for which you wish to pull information.  The Zillow-ID for the 314 Wood Hollow property is *36086728*.

```{r}
l <- home_estimate("36086728", format = "list")
```

The Zillow API returns a lot of information.  Try something like this to pull the estimated property value.

```{r}
# Current value of the property
l$zestimate$response$zestimate$amount[[1]]
```

```{r list_structure, eval=FALSE, echo=FALSE}
str(l)
```

Try exploring the rest of list with on your own.  The structure (str) of the list is available in the [Appendix](#appendix).

### Step 3. Archive the data

Switch the format of the data returned from the Zillow API to "xml," a more suitable format for archiving the data.  Then use R functions from the __xml2__ package to save to an archive directory.

```{r}
x <- home_estimate("36086728", format = "xml")
write_xml(x, glue('{zillow_dir}/36086728-{ts}.xml'))
```

HINT: Set up a Scheduled Task to automate this simple operation on a recurring basis.

### Step 4. Plot accumulated data

After you have some data accumulated over time for a single property, you will be ready to plot the information.  Here is a starter function.  Feel free to modify to suit your needs.

```{r, fig.width=7.2, fig.height=2}
homer::plot_zillow_directory(zillow_dir, strip_font_size = 12, nudge_y = 800, value_size = 2.6)
```

__Multiple Properties__ in the archive directory are treated as "facets" on the plot without any additional code. 

<a name="appendix"></a>

### Appendix

```{r list_structure}
```
